\documentclass[9pt, a4paper]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage[left=1.2cm, right=1.2cm, top=1.5cm, bottom=1cm]{geometry}
\usepackage{array} % Required for custom column alignment
\usepackage{enumitem}
\usepackage{fontspec} 
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,  % This removes the boxes around links
  linkcolor=blue,   % Customize the color of internal links
  urlcolor=blue,    % Customize the color of URLs
}
% Set the main font to DejaVu Sans
\setmainfont{DejaVu Sans}
% Remove indentation from the main text
\setlength{\parindent}{0pt}

\begin{document}

\begin{minipage}[t]{0.35\textwidth}
  \begin{LARGE}Pawan Kumar\end{LARGE} \\
  B.Tech. (Electrical Engineering) \\
  Indian Institute of Technology Roorkee
\end{minipage}%
\hfill % Pushes the following minipage to the right
%  \hspace{4cm}
\begin{minipage}[t]{0.30\textwidth} % Adjust the width as needed
  Contact No: +919472040084 \\
  Email: \href{mailto:iampawan0801@gmail.com}{iampawan0801@gmail.com} \\
  LinkedIn: \href{https://www.linkedin.com/in/singhpawank/}{singhpawank}
\end{minipage}

\vspace{5pt}

\section*{\rule{3.5cm}{1.5pt} \normalfont{Area of Interest}}

\vspace{-8pt}

Data Structures and Algorithms, Software Development, Machine Learning

\vspace{-8pt}

% Education Details
\section*{\rule{3.5cm}{1.5pt} \normalfont{Education}}

\vspace{-15pt}

\begin{table}[htb]
  \label{tab:example}
  \renewcommand{\arraystretch}{1.5} % Increase vertical padding
  \begin{tabular}{|>{\centering}p{1.5cm}|>{\raggedright}p{4cm}|>{\raggedright}p{8.5cm}|c|} % Use X columns to expand to full page width
    \hline
    Year & \centering Degree/Examination & \centering Institution/Board & CGPA/Percentage  \\
    \hline
    2023 & B.Tech. & Indian Institute of Technology Roorkee & 7.856 \\
    \hline
    2018 & Intermediate (Class XII) & Sarvoday High School, Samastipur(BSEB) & 75\%\\
    \hline
    2016 & Matriculate (Class X) & Green Valley International School, Malinagar(CBSE) & 9.00 \\
    \hline
  \end{tabular}
\end{table}

\vspace{-20pt}


% Internship
\section*{\rule{3.5cm}{1.5pt} \normalfont{Internship}}

\vspace{-22pt}
\subsection*{ \normalfont
 \begin{flushleft}
  \begin{normalsize}\textbf{Cyber security Engage} | Microsoft \hfill May 2022 - June 2022 \end{normalsize}
 \end{flushleft}
}
\vspace{-12pt}

\begin{itemize}[noitemsep]
  \item Learnt about various concepts of cyber security like computer forensics, defending against critical threats, reverse
  engineering, decompiling, disassembling, IDS, malware analysis tools, password sniffing, wireshark, DoS \& DDoS.
  \item Analysed cyber security challenges in smart grids, preventions and how to respond to cyber incidents.
\end{itemize}

\vspace{-20pt}

% Projects

\section*{\rule{3.5cm}{1.5pt} \normalfont{Projects}}

\vspace{-22pt}

\subsection*{ \normalfont
\begin{flushleft}
  \begin{normalsize}\textbf{Feedback Prediction System} | ArIES, IIT Roorkee \hfill Feb 2022 - April 2022 \end{normalsize}
\end{flushleft}
}
\vspace{-12pt}
\begin{itemize}[noitemsep]
  \item Developed a mobile application which provides feedback based on users' verbal reviews using Sentiment Analysis.
  \item Implemented the mobile app to collect users' audio reviews, transcribe them into text, and save them to the database.
  \item Created a web application to implement a Rest API using Django Rest Framework and a relational database.
  \item Performed text pre-processing, and designed and modelled ML algorithms to determine the sentiment polarity of the data.
\end{itemize}

\vspace{-40pt}

\subsection*{ \normalfont
\begin{flushleft}
  \begin{normalsize}\textbf{News oriented stock price trend prediction } | DoMS, IIT Roorkee \hfill March 2022 – May 2022 \end{normalsize}
\end{flushleft}
}
\vspace{-12pt}
\begin{itemize}[noitemsep]
  \item Worked on predicting trends in the stock market based on news headlines using data preprocessing and ML algorithms.
  \item Performed data segmentation and cleaning by tokenising, removing stop words and lemmatisation.
  \item Implemented the Logistic Regression and Support Vector Machine (SVMs) after cleaning the dataset.
\end{itemize}

\vspace{-40pt}

\subsection*{ \normalfont
\begin{flushleft}
  \begin{normalsize}\textbf{Path Planning of UAVs} | Electrical Engineering Department, IIT Roorkee \hfill August 2022 – April 2023 \end{normalsize}
\end{flushleft}
}
\vspace{-12pt}
\begin{itemize}
  \item Developed an unimpeded, reasonably priced route for an unmanned aerial vehicle, with both static and moving obstacles
    between the source and the destination, considering factors like distance, time and battery life of UAVs etc.
\end{itemize}

\vspace{-40pt}
\subsection*{ \normalfont
\begin{flushleft}
  \begin{normalsize}\textbf{Keeper App} | Web Development Bootcamp \hfill June 2023 \end{normalsize}
\end{flushleft}
}
\vspace{-12pt}
\begin{itemize}
  \item Developed a web application that allows users to store and manage important information effortlessly using ReactJS.
\end{itemize}

\vspace{-20pt}


% Skills

\section*{\rule{3.5cm}{1.5pt} \normalfont\begin{large} Skills \end{large}}

\vspace{-20pt}

\begin{table}[htb]
  \label{tab:Skills}
  \renewcommand{\arraystretch}{1.2} % Increase vertical padding
  \begin{tabular}{>{\raggedleft}p{95pt} >{}p{14.4cm} } 
    
    Computer languages & C++, Python, SQL, HTML, CSS, JavaScript    \\
    
    Software Packages &  Git, PyCharm, VS Code, Node.js, React, ExpressJs, Mongodb, Sci-kit Learn  \\ 
    
    Additional Courses & Operating System Fundamentals, Machine Learning, Data Mining \\ 
    
    Languages Known & English (SRW), Hindi (SRW) \\
    
  \end{tabular}
\end{table}

\vspace{-24pt}
% Awards / Scholarships / Academic Achievements

\section*{\rule{3.5cm}{1.5pt} \normalfont\begin{large} Awards / Scholarships / Academic Achievements \end{large}}

\vspace{-10pt}

\begin{itemize}[noitemsep]
  \item Global Rank 533 in Google Kickstart Round G 2022
  \item  Secured rank 11 in CodeChef Starters Division 3, February 2022
  \item  Secured rank 527 in Newton's Grand coding challenge June 2022
  \item  Secured rank 853 in Codechef Cook-Off Division 2, February 2022
  \item  Secured rank 1010 in Codeforces Round \#817
  \item  Secured rank 2347 in Google Kickstart Round A, March 2022 out of 17000+ participants
  \item All India Rank 4406, Joint Entrance Examination Advanced 2019
  \item Rank 140 in Bihar Combined Entrance Competitive Examination 2018
\end{itemize}

\vspace{-20pt}

\section*{\rule{3.5cm}{1.5pt} \normalfont \begin{large} Positions of Responsibility \& Extra Curricular \end{large}}

\vspace{-22pt}

\subsection*{ \normalfont
\begin{flushleft}
  \begin{normalsize}\textbf{Competitive Programmer} | Online Judges \hfill April 2020 - present \end{normalsize}
\end{flushleft}
}
\vspace{-12pt}
\begin{itemize}[noitemsep]
  \item Active member on Codechef and Codeforces. Codechef Max Rating: 1727 (handle: singhpawank), Codeforces Max Rating:1442 (handle: pawan\_k).
\end{itemize}





\end{document}
